Wait-free Queues with Polylogarithmic Step Complexity

### 2022-09-13 thesis/thesis.tex
minor changes

\Function{boolean}{Refresh()}{}
\State \tt{h= \head} \label{readHead}
%\State \tt{hp= parent.\head} \label{readParentHead1}
%\If{\nf{blocks[h]!=null}}
%\State \tt{CAS(blocks[h].super, null, hp)} \label{helpSuper1}
%\EndIf
\ForEach{\tt{dir} {\keywordfont{in}} \tt{\{left, right\}}} \label{startHelpChild1}
\State \tt{h\sub{dir}= dir.\head} \label{readChildHead}
\If{\nf{dir.blocks[h\sub{dir}]!=null}}
\State \tt{CAS(dir.blocks[h\sub{dir}].super, null, h)}
\State \tt{CAS(dir.head, h\sub{dir}, h\sub{dir}+1)}
\EndIf
\EndFor \label{endHelpChild1}
\State \tt{new= \Call{CreateBlock}{h}} \label{invokeCreateBlock}
\If{\tt{new.num==0}} \Return{\tt{true}} \label{addOP} 
%\cmt{Created block contains nothing.}
\EndIf
\State{\tt{result= blocks.tryAppend(new, h)}} \label{cas}
\State \tt{hp= parent.\head} \label{readParentHead}
\State \tt{\Call{CAS}{n.blocks[h].super, null, hp}} \label{setSuper1}
\State \tt{\Call{CAS}{\head, h, h+1}} 
%\cmt{Even if another process wins, help to increase the \tt{\head}. The winner might have fallen sleep before increasing \tt{\head}.} \label{incrementHead2}
\State \Return{ \tt{result}}

@@

\begin{corollary}
  After a successful \nf{TryAppend(new,h)}, \nf{n.blocks[h].super} is set before the next succseful \nf{n.Refresh} or the second next succesful \nf{n.parent.Refresh()}.
\end{corollary}
\begin{proof}
\nf{n.TryAppend(h+1)}cannot happen unless \nf{n.head} is incremented from \nf{h} to \nf{h+1}. The latter case is explained in the next page.  
\end{proof}

@@

\begin{lemma}\label{superRange} If $\nf{b.super} \neq \nf{null}$ then, the superblock of \nf{b} is in \nf{n.parent.blocks[b.super-1..b.super+2]}.
\end{lemma}
\begin{proof}
Let us explain the possible cases of setting \nf{super} of block \nf{b} in node \nf{n}.

>>>>

\Function{boolean}{Refresh()}{}
\State \tt{h= \head} \label{readHead}
%\State \tt{hp= parent.\head} \label{readParentHead1}
%\If{\nf{blocks[h]!=null}}
%\State \tt{CAS(blocks[h].super, null, hp)} \label{helpSuper1}
%\EndIf
\ForEach{\tt{dir} {\keywordfont{in}} \tt{\{left, right\}}} \label{startHelpChild1}
\State \tt{h\sub{dir}= dir.\head} \label{readChildHead}
\If{\nf{dir.blocks[h\sub{dir}]!=null}}
\State \tt{dir.blocks[h\sub{dir}].super.CAS(null, h)}
\State \tt{dir.head.CAS(h\sub{dir}, h\sub{dir}+1)}
\EndIf
\EndFor \label{endHelpChild1}
\State \tt{new= \Call{CreateBlock}{h}} \label{invokeCreateBlock}
\If{\tt{new.num==0}} \Return{\tt{true}} \label{addOP} 
%\cmt{Created block contains nothing.}
\EndIf
\State{\tt{result= blocks[h].CAS(null, new)}} \label{cas}
\State \tt{hp= parent.\head} \label{readParentHead}
\State \tt{n.blocks[h].super.\Call{CAS}{null, hp}} \label{setSuper1}
\State \tt{\head.\Call{CAS}{h, h+1}} 
%\cmt{Even if another process wins, help to increase the \tt{\head}. The winner might have fallen sleep before increasing \tt{\head}.} \label{incrementHead2}
\State \Return{ \tt{result}}

@@

\begin{lemma}
  After a successful \nf{TryAppend(new,h)}, \nf{n.blocks[h].super} is set before the next succseful \nf{n.Refresh} or the second next succesful \nf{n.parent.Refresh()}. Superblock of \nf{b} is in \nf{n.parent.blocks[b.super-1..b.super+2]}.
\end{lemma}
\begin{proof}
\nf{n.TryAppend(h+1)}cannot happen unless \nf{n.head} is incremented from \nf{h} to \nf{h+1}. The latter case is explained in the next page.  
\end{proof}

@@

\begin{lemma}\label{superRange}  
\end{lemma}
\begin{proof}
Let us explain the possible cases of setting \nf{super} of block \nf{b} in node \nf{n}. \nf{b.super} is set by an instance of \nf{n.Refresh} or \nf{n.parent.Refresh}. Since Lines \ref{} setting the \nf{super} is done before incrementing the \nf{head}, so if we know \nf{head} has advanced the super has to be set before.
